R Notebook

### 2018-02-21 paper/docs/04_Modelresults.Rmd
k=40

I conduct a STM (Strucutral Topic Molde) estimation on a sample of 11,919 online news articles from seven news provider about domestic politics: Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, Stern.de, ZEIT ONLINE, Tagesschau.de. The articles are dated from 01.06.2017 to 31.12.2017 (German federal elections took place on 24th of September 2017.). I first extract all online articles using the the [Eventregistry API](http://eventregistry.org/documentation). Then all articles from the section "domestic policy" are filtered by checking the URL structure.

@@

sagelabs$cov.betas[[3]]$problabels[,1:5]
```

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "B90/Die Grüne, coalition talks", 4, "EU policies", 
                   5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election results", 8, "CSU, Seehofer, Söder", 
                   9, "Welt, Deutschland, Menschen", 10, "Parliament (Bundestag)", 
                   11, "W.Schäuble", 12, "Refugees in GER", 13, "G.Schröder, IT Topics", 
                   14, "B90/Die Grüne, climate/refugee policy", 
                   15, "D.Trump, Israel", 16, "Great coalition", 17, "AfD, in media", 
                   18, "Jamaica coalition", 
                   19, "Rubbish", 20, "Terror attack Amri", 21, "German armed forces, Mali, Helicopter", 
                   22, "Muslim, Ditib", 23, "Elections in Niedersachsen", 24, "CDU, Twitter, Saxony", 
                   25, "Europa", 26, "Bundestag, Laws", 
                   27, "Surveys, public statistics", 28, "Election polls", 
                   29, "AfD", 30, "Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen", 
                   32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia", 
                   34, "Left- & Right-wing Terror", 35, "CDU/CSU H.Seehofer, Obergrenze",
                   36, "Church", 37, "Car industry, Stuttgart", 38, "AfD, F.Petry", 39, "Statistics, welfare policy",
                   40, "J.Spahn"), ncol=2, byrow=T)

@@

```{r fig.height=11, fig.width=5}
topic <- 12

@@

In order to get an initial overview of the results, Figure \ref{fig_topic_proportion} displays the topics ordered by their expected frequency across the corpus (left side of the Figure) and the expected proportion of a topic in public media minus the expected proportion of topic use in private media (right side of the Figure). Thus topics more associated with public media appear to the right of zero. To assign a label to each topic, I looked at the most frequent words in that topic and the most representative articles

@@

```{r}
frequency <- as.data.frame(colMeans(stmOut$theta)) %>% 
  mutate(frequency = colMeans(stmOut$theta),
    topic=paste(topics[,1],topics[,2], sep=": "))

@@

freq <- freq %>%
  left_join(., topics.df, by = "topic") %>%
  mutate(topic = topic_name) %>%
  left_join(., frequency %>% select(topic, frequency),
            by = "topic")
```

@@

```{r fig.height=6}
p1 <- ggplot(frequency, aes(x=reorder(topic, frequency), y=frequency)) + 
    geom_col(fill=col[1], alpha=0.8) +
    coord_flip() +
    labs(x="", y="expected frequency") +
    theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10))

@@

```{r fig.height=8, fig.width=12}
p1 <- coeff %>% 
  filter(parameter %in% stmOut$settings$covariates$yvarlevels) %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  scale_x_discrete(position = "top") +
  coord_flip() +
  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
  labs(x="", fill="significant at the 5% level") +
  theme(legend.position = "top", 
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle=90))

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
# Tokenize text
token <- btw.2 %>%
  filter(gamma >= 0.9) %>%
  filter(topic != 19) %>%
  unnest_tokens(word, text)

>>>>

I conduct a STM (Strucutral Topic Model) estimation on a sample of 11,919 online news articles from seven news provider about domestic politics: Bild.de, DIE WELT, FOCUS ONLINE, SPIEGEL ONLINE, Stern.de, ZEIT ONLINE, Tagesschau.de. The articles are dated from 01.06.2017 to 31.12.2017 (German federal elections took place on 24th of September 2017.). I first extract all online articles using the the [Eventregistry API](http://eventregistry.org/documentation). Then all articles from the section "domestic policy" are filtered by checking the URL structure.

@@

sagelabs$cov.betas[[3]]$problabels[,1:6]
```

```{r}
topics <- matrix(c(1, "SPD, M.Schulz", 2, "A.Merkel vs. Schulz", 3, "B90/Die Grüne, coalition talks", 
                   4, "EU topics: Diesel, Glyphosat, toll", 5, "H.Kohl", 6, "A.Merkel", 7, "Federal Election results",
                   8, "Party congress (CSU and DIE LINKE)", 9, "General societal issues", 
                   10, "Information on Federal elections (e.g. Wahlomat, election programmes)",  
                   11, "W.Schäuble, F.Steinmeier", 12, "Refugees in GER", 13, "Auffangbecken ('Find us on Twitter')",
                   14, "B90/Die Grüne, climate/refugee policy", 15, "D.Trump, Israel, G20", 
                   16, "Great coalition, minority government", 17, "AfD, in media", 18, "Jamaica coalition", 
                   19, "Rubbish", 20, "Mix (Amri, Berlin, Court)", 21, "German armed forces, Mali, Helicopter", 
                   22, "Mix (Ditib, Weather, DB)", 23, "Elections in Niedersachsen", 24, "CDU, regional politics (Saxony)", 
                   25, "Mix (Europa, political talkshows)", 26, "Votes in the Bundestag", 
                   27, "Mix, Surveys, public statistics", 28, "Election polls", 
                   29, "AfD in parliament", 30, "Mix: Sexism, Court sentences, NSU trial", 31, "German armed forces, v.d.Leyen", 
                   32, "G20 in Hamburg", 33, "Diplomatic relations w Turkey, Russia", 
                   34, "Terror in GER, Left- & Right-wing", 35, "CDU/CSU H.Seehofer, Obergrenze",
                   36, "Church, Family", 37, "Car industry, Stuttgart (Mix)", 38, "AfD, F.Petry", 39, "Statistics, welfare policy",
                   40, "J.Spahn"), ncol=2, byrow=T)

@@

```{r fig.height=11, fig.width=5}
topic <- 40

@@

In order to get an initial overview of the results, the figure below displays the topics ordered by their expected frequency across the corpus (left side of the Figure) and the expected proportion of a topic in public media minus the expected proportion of topic use in private media (right side of the Figure). Thus topics more associated with public media appear to the right of zero. To assign a label to each topic, I looked at the most frequent words in that topic and the most representative articles.

Keep only those articles, that are clear

```{r}
keep <- c(1,2,3,4,5,6,7,12,14,15,16,17,18,21,23,24,28,29,31,32,33,34,35,38,40)
```

@@

```{r}
frequency <- as.data.frame(colMeans(stmOut$theta)) %>%
  mutate(frequency = colMeans(stmOut$theta),
         topic = topics[,1],
         topic_name=paste(topics[,1],topics[,2], 
                          sep=": ")) %>%
  filter(topic %in% keep)

@@

freq <- freq %>%
  left_join(., topics.df, by = "topic") %>%
  filter(topic %in% keep) %>%
  mutate(topic = topic_name) %>%
  left_join(., frequency %>% select(topic, frequency),
            by = "topic")
```

@@

```{r fig.height=6}
p1 <- ggplot(frequency, aes(x=reorder(topic_name, frequency), y=frequency)) + 
    geom_col(fill=col[1], alpha=0.8) +
    coord_flip() +
    labs(x="", y="expected frequency") +
    theme(axis.text.x = element_text(size=8),
          axis.text.y = element_text(size=11),
          axis.title = element_text(size=10))

@@

```{r fig.height=8, fig.width=12}
p1 <- coeff %>% 
  filter(topic %in% keep) %>%
  filter(parameter %in% stmOut$settings$covariates$yvarlevels) %>%
  ggplot(aes(x = reorder(topic_name,topic, decreasing=F), y = Estimate, fill=factor(signifcant))) +
  geom_col() +
  scale_fill_manual(values = col[c(2,1)]) +
  scale_x_discrete(position = "top") +
  coord_flip() +
  facet_wrap(~parameter, ncol = 8, scales = "free_x") +
  labs(x="", fill="significant at the 5% level") +
  theme(legend.position = "top", 
        axis.text.y = element_text(size=9),
        axis.text.x = element_text(angle=90))

@@

```{r, message=FALSE, warning=FALSE, include=FALSE}
# Tokenize text
token <- btw.2 %>%
  filter(gamma >= 0.9) %>%
  filter(topic %in% keep) %>%
  unnest_tokens(word, text)

### 2018-02-21 paper/docs/backup.Rmd
k=40

>>>>

## 3.4 Distance metric
Compute different metrices and compare them.

Compute the Jensen Shannon divergence of the word-topic probability. The K-by-V (number of words in the vocabulary) matrix logbeta contains the natural log of the probability of seeing each word conditional on the topic.

```{r}
k <- stmOut$settings$dim$K
p <- length(stmOut$settings$covariates$yvarlevels)
```

```{r}
## Find all combinations of ylevel
comb.matrix <- matrix(0, 
                      nrow= p^2, 
                      ncol = 2)

z <- 1
for (i in 1:p) {
  for (j in 1:p) {
    comb.matrix[z,1] <- stmOut$settings$covariates$yvarlevels[i]
    comb.matrix[z,2] <- stmOut$settings$covariates$yvarlevels[j]
    z <- z+1
  }
}
```

### Calculate L1 Norm
```{r}
# Create empty matrix
l1.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
names(l1.matrix) <- 1:k

# Populate matrix with JSD Values
z <- 1
for (i in 1:p) {

    #print(paste("ylevel = ", i))
    base <- exp(stmOut$beta$logbeta[[i]])
    compare1 <- exp(stmOut$beta$logbeta[[1]])
    compare2 <- exp(stmOut$beta$logbeta[[2]])

  for (j in 1:k) {

    #print(paste("topic = ", j))
    l1.matrix[z,j] <- sum(abs(base[j,]-compare1[j,]))
    l1.matrix[z+1,j] <- sum(abs(base[j,]-compare2[j,]))

  }
    z <- z+p
}

```

```{r}
## Create DF
l1.df <- as.data.frame(l1.matrix) 
colnames(l1.df) <- 1:k

l1.df <- l1.df %>% 
  mutate(News1 = comb.matrix[,1],
         News2 = comb.matrix[,2]) %>%
  melt(.,id=c("News1","News2"), value.name="L1Norm",
       variable.name = "topic") %>%
  mutate(topic = as.integer(topic)) %>%
  left_join(., topics.df, by="topic")
```

### Calculate Cosine Similarity
```{r}
# Create empty matrix
cosine.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
names(cosine.matrix) <- 1:k

# Populate matrix with JSD Values
z <- 1
for (i in 1:p) {

    #print(paste("ylevel = ", i))
    base <- exp(stmOut$beta$logbeta[[i]])
    compare1 <- exp(stmOut$beta$logbeta[[1]])
    compare2 <- exp(stmOut$beta$logbeta[[2]])

  for (j in 1:k) {

    #print(paste("topic = ", j))
    cosine.matrix[z,j] <- CosSim(base[j,],compare1[j,])
    cosine.matrix[z+1,j] <- CosSim(base[j,],compare2[j,])

  }
    z <- z+p
}

```

```{r}
## Create DF
cosine.df <- as.data.frame(cosine.matrix) 
colnames(cosine.df) <- 1:k

cosine.df <- cosine.df %>% 
  mutate(News1 = comb.matrix[,1],
         News2 = comb.matrix[,2]) %>%
  melt(.,id=c("News1","News2"), value.name="CosineSimilarity",
       variable.name = "topic") %>%
  mutate(topic = as.integer(topic)) %>%
  left_join(., l1.df, by=c("News1","News2","topic"))
```

### Calculate KLD
```{r}
# Create empty matrix
kld.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
names(kld.matrix) <- 1:k

# Populate matrix with JSD Values
z <- 1
for (i in 1:p) {

    #print(paste("ylevel = ", i))
    base <- exp(stmOut$beta$logbeta[[i]])
    compare1 <- exp(stmOut$beta$logbeta[[1]])
    compare2 <- exp(stmOut$beta$logbeta[[2]])

  for (j in 1:k) {

    #print(paste("topic = ", j))
    kld.matrix[z,j] <- KLD(base[j,],compare1[j,])
    kld.matrix[z+1,j] <- KLD(base[j,],compare2[j,])

  }
    z <- z+p
}
```

```{r}
## Create DF
kld.df <- as.data.frame(kld.matrix) 
colnames(kld.df) <- 1:k

kld.df <- kld.df %>% mutate(News1 = comb.matrix[,1],
         News2 = comb.matrix[,2]) %>%
  melt(.,id=c("News1","News2"), value.name="KLD",
       variable.name = "topic") %>%
  mutate(topic = as.integer(topic)) %>%
  left_join(., cosine.df, by=c("News1","News2","topic"))
```

### Calculate JSD
```{r}
# Create empty matrix
jsd.matrix <- matrix(0, nrow = nrow(comb.matrix), ncol = k)
names(jsd.matrix) <- 1:k

# Populate matrix with JSD Values
z <- 1
for (i in 1:p) {

    #print(paste("ylevel = ", i))
    base <- exp(stmOut$beta$logbeta[[i]])
    compare1 <- exp(stmOut$beta$logbeta[[1]])
    compare2 <- exp(stmOut$beta$logbeta[[2]])

  for (j in 1:k) {

    #print(paste("topic = ", j))
    jsd.matrix[z,j] <- JSD(base[j,],compare1[j,])
    jsd.matrix[z+1,j] <- JSD(base[j,],compare2[j,])

  }
    z <- z+p
}
```

```{r}
## Create DF
jsd.df <- as.data.frame(jsd.matrix) 
colnames(jsd.df) <- 1:k

distance.df <- jsd.df %>% mutate(News1 = comb.matrix[,1],
         News2 = comb.matrix[,2]) %>% 
  melt(.,id=c("News1","News2"), value.name="JSD",
       variable.name = "topic") %>%
  mutate(topic = as.integer(topic)) %>%
  left_join(., kld.df, by=c("News1","News2","topic"))

rm(l1.df, jsd.df, cosine.df, kld.df)
```

### Plot 
```{r}
cols <- rev(brewer.pal(11, 'RdYlBu'))

p1 <- distance.df %>%
  filter(!topic %in% c("11","15")) %>%
  filter(News1!=News2) %>%
  filter(News1=="private") %>%
  ggplot(aes(News1, reorder(factor(topic_name),JSD), fill = JSD)) + 
  geom_tile() +
  scale_fill_gradientn(colours = cols) +
  labs(x="", y="") +
  theme_bw(base_family = "Roboto", base_size = 11) +
  theme(axis.text.x = element_blank(),
        legend.position = "top",
        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
        axis.ticks = element_line(colour = 'transparent'))

p2 <- distance.df %>%
  filter(!topic %in% c("11","15")) %>%
  filter(News1!=News2) %>%
  ggplot(aes(News1, reorder(factor(topic_name),JSD), fill = KLD)) + 
  geom_tile() +
  scale_fill_gradientn(colours = cols) +
  labs(x="", y="") +
  theme_bw(base_family = "Roboto", base_size = 11) +
  theme(axis.text.y = element_blank(),
        legend.position = "top",
        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
        axis.ticks = element_line(colour = 'transparent'))

p3 <- distance.df %>%
  filter(!topic %in% c("11","15")) %>%
  filter(News1!=News2) %>%
  filter(News1=="private") %>%
  ggplot(aes(News1, reorder(factor(topic_name),JSD), 
             fill = CosineSimilarity)) + 
  geom_tile() +
  scale_fill_gradientn(colours = cols) +
  labs(x="", y="") +
  theme_bw(base_family = "Roboto", base_size = 11) +
  theme(axis.text = element_blank(),
        legend.position = "top",
        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
        axis.ticks = element_line(colour = 'transparent'))

p4 <- distance.df %>%
  filter(!topic %in% c("11","15")) %>%
  filter(News1!=News2) %>%
  filter(News1=="private") %>%
  ggplot(aes(News1, reorder(factor(topic_name),JSD), 
             fill = L1Norm)) + 
  geom_tile() +
  scale_fill_gradientn(colours = cols) +
  labs(x="", y="") +
  theme_bw(base_family = "Roboto", base_size = 11) +
  theme(axis.text = element_blank(),
        legend.position = "top",
        plot.background = element_rect(fill = 'transparent', colour = 'transparent'),
        strip.background = element_rect(fill = 'transparent', colour = 'transparent'),
        axis.ticks = element_line(colour = 'transparent'))

(p1 | p2 | p3 | p4 )

ggsave(filename = "../figs/distance.png", device = "png",width = 12, height = 8,
dpi = 600)
```

### 2018-02-21 paper/writing/doc.tex
k=40

% ----------------------
% Model Results
% ----------------------
\subsection{Interpretation}

@@

A way to summerize the topics in an interpretable way is to use the most frequent terms within a topic \citep{chang_reading_2009}, but the exclusivity of words to topics is equally important for communicating content. \citep{bischof_summarizing_2012} consider the harmonic mean of the words's rank in terms of exclusivity and frequency as a summary for a word's contribution to a topic. It is important to take both of these properties into account, as frequent words are often simply functional words that are necessary to discuss a topic. While completely exclusive words can be so rare that their information content is too low. \citep{roberts_stm:_2016} refer to this as the FREX (FRequency and EXclusivity) metric.

\begin{align}
	FREX_{k,\nu} = (\frac{\omega}{ECDF(\beta_{k,\nu}/\sum^K_{j=1}\beta_{j,\nu}}+\frac{1-\omega}{ECDF(\beta_{k,\nu}})^{-1},
\end{align}

with $\boldsymbol{B}$ denoted as the $KxV$ matrix of topic-conditional term probabilities. The first part of the equation calculates the frequency score  given by the empirical CDF of the word in it's topic distribution. Exclusivity is calculated by column-normalizing the beta matrix (thus representing the conditional probability of seeing the topic given the word). $\omega$ balances the influence of frequency and exclusivity and is set to $0.5$

\section{Empirical Evaluation}

@@

%\begin{landscape}
%\begin{figure}[H]
%\centering
%	\caption{Sample articles}
%	\includegraphics[width=\linewidth,height=.9\textheight,keepaspectratio]{../figs/topic-classification-sample.png}	
%	\label{fig_classification}
%\end{figure}
%\end{landscape}

@@

\section{Sentiment Analysis}

>>>>

% ----------------------
% Model Results
% ----------------------
\subsection{Empirical Evaluation}

@@

@@

@@

\section{Distance Metric}

Since the topic distribution of a text is a simple mapping of text space, similarity of two texts can be measured by computing the topic distribution. KL distance is the measurement of “difference” between two probabilities.

We use a probability distribution distance metric related to Jensen-Shannon divergence (JSD) to compare the word-topic distribution. Jensen-Shannon Divergence is a positive definite measure, satisfying the following conditions: $D_{js}(a,b) \geq 0$, $D_{js}(a,b)=0$ iff $(a=b)$. It is also symmetric: $D_{js}(a,b)=D_{js}(b,a)$. Let $p(x)$ and $q(x)$ be two probability density functions, the Jensen-Shannon distance $D_{js}(p,q)$ between this two distributions is defined as:

\begin{align*}
	D_{js}(p,q)=\frac{1}{2}D_{KL}(p,\frac{p+q}{2})+\frac{1}{2}D_{KL}(q,\frac{p+q}{2})
\end{align*}

where $D_{KL}$ is the Kullback-Leibler divergence between $p$ and $q$ defined as:

\begin{align*}
	D_{KL}(p,q)=\sum_{i=1}^T p_i ln \frac{p_i}{q_i}
\end{align*}

Since $D_{js}$ does not satisfy the triangular inequality condition $D_{js}(a,c)\leq D_{js}(a,c)+D_{js}(b,c)$, the JSD is not considered to be a real metric. On the other hand, the square root of JSD is a real distance metric \citep{endres_new_2003}. This is the reason why we use the square root and not JSD itself.

\section{Sentiment analysis}

The idea of Sentiment analysis is to determine the attitude of a writer through online text data toward certain topic or the overall tonality of a document.

### 2018-02-21 paper/writing/doc_backup.tex
k=40

>>>>

\section{Competitor Analysis}
\subsection{Competitor analysis}

Users can access a news website either directly or through an intermediary, such as search engines or social media.  As Figure \ref{fig_traffic} illustrates\footnote{The figure shows the percentage of total traffic by source for the time period 18.12.2017-18.01.2017}, direct access\footnote{Direct traffic includes: Direct navigation (Someone types the website URL into a browser); Bookmarks (Clicks on a bookmark/favorite link in a browser); Email (Clicks on links in desktop email clients)} to a website is the main source of traffic for most news providers. In the case of Bild.de, the percentage is 85\%. Also n-tv.de (79\%), SPIEGEL ONLINE (76\%) and Tagesschau.de (75\%) get most of their traffic via the direct route. Other providers are more reliant on intermediaries, mainly search engines. FOCUS ONLINE, DLF and Handelsblatt.com, for example, obtain between 40\% and 45\% of its traffic via search engines. Thus, an important question is, which organic search keywords send traffic to a website. Figure \ref{fig_searchtraffic} displays the percentage of organic search referrals to a specific website that come from this keyword.\footnote{Percentage of organic search referrals in major search engines over the time span Jun-Dec 2017.} E.g., 0.78\% of all organic search referrals to Handelsblatt.com come from the keyword "handelsblatt". It is not surprising that the provider's name is the keyword that generates the majority of traffic for most of the news pages. However, different topics as well as names of other providers are hidden among the top 10 keywords.

\begin{figure}[H]
	\caption{Traffic Sources}
	\begin{center}
		\includegraphics[width=0.8\textwidth]{../figs/traffic_source.png}
		\label{fig_traffic}
	\end{center}
\end{figure}

\begin{figure}[H]
	\caption{Search traffic \%}
	\begin{center}
		\includegraphics[width=0.8\textwidth]{../figs/search_traffic.png}
		\label{fig_searchtraffic}
	\end{center}
\end{figure}

Assuming that each search query is in itself a market where providers compete for traffic, the share of search queries for a keyword that has led visitors to a news page is the market share of that provider. In this context, figures \ref{fig_keywords1} and \ref{fig_keywords2} show the market share of providers for different keywords.\footnote{The figures show the percentage of searches for a keyword that sent traffic to a website in major search engines over the time span Jun-Dec 2017.} Nearly 15\% of all search queries for the keyword "Bundestagswahl 2017" (federal elections 2017) were forwarded to DIE WELT. FOCUS ONLINE, faz.net and SPIEGEL ONLINE obtained a market share of 7\% - 8\%. For the keyword "Groko" (grand coalition between CDU/CSU and SPD), SPIEGEL ONLINE was able to gain the largest market share (17\%) in the past six months, followed by DIE WELT (\%10), FOCUS ONLINE (8\%) and Bild.de (7.5\%). Figure \ref{fig_keywords2} shows the market share of news pages for the keyword search for a specific party.

Contrary to figure \ref{fig_keywords1} , the x-axes in figure \ref{fig_keywords2} are scaled equally to show not only the market share of news sites for a specific party-keyword, but also for which party this provider has the largest market share. For example, we can see that the market share of sueddeutsche.de is largest for the keyword "Die Grünen". However, the biggest market share among the listed news providers for this keyword has Zeit.de. The largest market share for the keyword "AfD" can be found at DIE WELT, followed by SPIEGEL ONLINE. The proportion of public news providers is comparatively low for all keywords.

\begin{figure}[H]
	\begin{center}
			\includegraphics[width=.8\textwidth]{../figs/keywords1.png}
			\caption{Keyword market share for policy topics / general}
			\label{fig_keywords1}
	\end{center}
\end{figure}

\begin{figure}[H]
	\begin{center}
			\includegraphics[width=.8\textwidth]{../figs/keywords2.png}
			\caption{Keyword market share for party-keywords}
			\label{fig_keywords2}
	\end{center}
\end{figure}
